### 2022-07-17 README.Rmd
Update map
add funding TML

@@

>>>>

#### ENMAC Scenario

See [here](region_enmac4_quiet.html) for full map.

```{r}
# knitr::include_url("m_rnet_enmac_region_fastest.html")
```

<iframe src="region_enmac4_quiet.html" width="800" height="400px" data-external="1">
</iframe>

See [here](articles/propotype.html) for results for each Municipality.

#### E-bike Scenario

<!-- todo -->

#### Intermodality Scenario

<!-- todo -->

@@

# Funding

This project is funded by [TML - Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/projetos-e-atividades/planos-e-estudos/rede-ciclavel-metropolitana-estudo-modelacao-e-ferramenta-de-apoio-ao-planeamento-e-decisao/).
